Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
jellin 3 induction

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}
^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] If every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

%\begin{lem}\label{lem:n-3s-admissible}
%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
%\end{lem}
%\begin{proof}
%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
%
 %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
%\begin{itemize}
%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
%\end{itemize}
%\end{proof}

@@

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either 
\begin{enumerate}
	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
	\item or $e_1' = \cdots = e_r' = 3$ and $r \geq 2$ or $g \geq 2$, and let $y_{1, 3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
\end{enumerate}
Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-\ord_{Q_i}
^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b1)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(b2)] If $(\sx',\halfcan',J)$ is not admissible, but $\{e_1,\ldots, e_n\} = \{3\},$ the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c1)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(c2)]  If $(\sx',\halfcan',J)$ is not admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.

	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations 
as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
We will only prove this in the harder case $(\sx, L', J)$ is admissible, as the case $e_1 = \cdots = e_r = 3$ is similar.

Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
question, with coarse spaces $X = X'$. 
\todo{possibly generalize these to arbitrary log  $\Delta \neq 0$ spin curves}
Define

@@

\noindent
and so we obtain an inclusion
\begin{align*}
	H^0(\sx', e_iL'-E_i + Q_j) \rightarrow H^0(\sx, e_iL - E_i) \subset 
H^0(\sx, e_iL).
\end{align*}\todo{Peter: should be $Q_i$?}

@@

Next, define $R_0 = R'$ and inductively define 
$$R_i = \begin{cases}
	R_{i - 1} &\text{ if }i \notin J\\
	R_{i - 1}[y_{i, e_i}] &\text{ otherwise.} 
\end{cases}$$

@@

Finally, to check (e), we will first show that $(\sx, J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

@@

\begin{cor}
\label{cor:raise-stacky-order}
Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ with $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}. Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of ramified points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
$$
e_i \begin{cases}
	= e_i' &\text{ if }i \notin J\\
	\leq e_i' &\text{ if } i \in J
\end{cases}$$
then Theorem ~\ref{thm:general_generators_relations} holds for $(\sx,\Delta,L)$
\end{cor}
\begin{proof}
For $t \leq i \leq r$. Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let 
$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.

>>>>

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally \todo{Aaron: Should the word minimally be removed here?} generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
	\item[(c)] Any set of generators for $I'$ together with 
		any set of relations with leading terms as in (b) 
		generate $I$.
\end{enumerate}
\end{lem}

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] First, 
	\begin{align*}
	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}.
	\end{align*}
		\item[(Ad-ii)] Second, every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] Third, we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

%\begin{lem}\label{lem:n-3s-admissible}
%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
%\end{lem}
%\begin{proof}
%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
%
 %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
%\begin{itemize}
%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (Ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
%\end{itemize}
%\end{proof}

@@

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$ and either 
\begin{enumerate}
	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
	\item or $\sigma$ is one of the signatures described in Remark ~\ref{rem:three-cases}, with $y_{1, 3} = y_{2,3} = \ldots, y_{r,3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
\end{enumerate}
Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-\ord_{Q_i}
^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
We will only prove this in the case (1), that $(\sx', L', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.

Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be the two log spin curves in 
question, with coarse spaces $X = X'$.
Define

@@

\noindent
and so we obtain an inclusion
\begin{align*}
	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subset 
H^0(\sx, e_iL).
\end{align*}

@@

Next, define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
$$R_i = \begin{cases}
	R_{i - 1} &\text{ if }i \notin J\\
	R_{i - 1}[y_{i, e_i}] &\text{ otherwise.} 
\end{cases}$$

@@

Finally, to check (d), we will first show that $(\sx, J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

@@

\begin{cor}
\label{cor:raise-stacky-order}
Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three cases}. Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}. Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of ramified points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
$$
e_i \begin{cases}
	= e_i' &\text{ if }i \notin J\\
	\leq e_i' &\text{ if } i \in J
\end{cases}$$
then Theorem ~\ref{thm:general_generators_relations} holds for $(\sx,\Delta,L)$
\end{cor}
\begin{proof}
For $t \leq i \leq r$. Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let 
$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
